---
title: "MATH 158 - Data Description and Descriptive Statistics"
author: "John King"
date: "due Thursday, Feb 8, 2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE, warning = FALSE,
                      fig.width = 7, fig.height = 3, 
                      fig.align = 'center')
library(tidyverse)
library(broom)
library(tidymodels)
library(mosaic)
library(ggplot2)

```



### Introduction to Data

The data from this project comes from [TidyTuesday](https://github.com/rfordatascience/tidytuesday/tree/master/data/2021/2021-03-02) and [fivethirtyeight](https://github.com/fivethirtyeight/superbowl-ads) on GitHub. This data is a collection of the top 10 companies who posted the most advertisements during the Superbowl between the years 2000 and 2020. Because of errors in data collection, seventeen of the videos had to be removed from the data. From this, we want to compare the different qualities in the video to the youtube performance after the event.

The observational unit is each individual advertisement, and there are 10 variables. The categorical variables are logical binary variables which identify as True or False. 

Quantitative Data

- Year: This variable indicates the year the Superbowl advertisement aired on TV. 

- View Count: This variable indicates how many youtube views the advertisement has received. 

- Like Count: This variable indicates how many youtube likes the advertisement has received.

- Dislike Count: This variable indicates how many youtube dislikes the advertisement has received.

- Comment Count: This variable indicates how many youtube comments the advertisement has received.

Categorical Data

- Funny: This variable indicates whether the advertisement is intended to be funny. 

- Celebrity: This variable indicates whether a celebrity is in the advertisement. 

- Danger: This variable indicates whether there is danger in the advertisement.

- Animals: This variable indicates whether there are animals in the advertisement.

- Use Sex: This variable indicates whether there is use of sexuality in the advertisement.

### Summary of Statistics

As mentioned above, the dataset looked at the 10 companies who prepared advertisements between 2000 and 2020. Out of these 10 companies, this first graph shows how many total advertisements they posted each year. This graph shoes that during this time span, there was a wide range of advertisements posted by these companies. It was interesting to see how consistent certain comapnies would post one or more  advertisements for every year in the Superbowl. 

```{r  fig.cap = "Advertisements by Year"}
maindata <- read.csv("Data - ExportedData.csv")
my_data <- as.data.frame(maindata)                   
ggplot(my_data, aes(x=year)) + geom_bar()

```


The second graph will show how many advertisements each company created for the span of Superbowls. It would be expected that companies selling beer, snacks, or cars would be the main leaders of this study. It was surprising to see the right skew of how much beer advertisements dominated the other leaders. 

```{r fig.cap = "Advertisements by Brand"}
maindata <- read.csv("Data - ExportedData.csv")
my_data <- as.data.frame(maindata)                   
ggplot(my_data, aes(x=brand)) + geom_bar()  
```

For the first table, I indicated some critical statistics encompassing all of the videos for each brand. By identifying the max column, we can see how certain brands like Doritos have very popular videos that skew their mean view count. However, Doritos, along with the NFL, still have some of the most consistent performing videos with much higher median values than the other brands. 
```{r fig.cap = "View Count by Brand"}
maindata <- read.csv("Data - ExportedData.csv")
my_data <- as.data.frame(maindata)
df6<-maindata %>%
  group_by(brand) %>%
  summarise(Min = min(view_count),
            Max=max(view_count), 
            mean = round(mean(view_count)), 
            median = round(median(view_count)))
df6
```

For Figure 3, I want to reveal the number of observations which identify as True or False, giving insight into how often each tactic was used to attract customers to their products. It was expected to see funny advertisements have such a high percentage, but the other categories were all consistent with each other.   

```{r fig.cap = "Percent True by Category"}

exset <- data.frame(
  category=c("funny","celebrity","danger","animals","use_sex") ,  
  percent_true=c(0.792, 0.329, 0.347, 0.426, 0.306 ))
ggplot(exset, aes(x=category, y=percent_true)) + 
  geom_bar(stat = "identity")
```

In this last table, I highlighted the mean and median number of views for advertisements based on responding True or False to each category. The mean values were skewed by an outlier which followed the characteristics with the highest number of views. However, the median values indicate that there could be lower views when using sexuality or celebrities in the advertisements. 

```{r fig.cap = "Total Views by Category"}
df7<-maindata %>% group_by(funny) %>% summarise(mean = round(mean(view_count)), 
median = round(median(view_count)))
df8<-maindata %>% group_by(celebrity) %>% summarise(mean = round(mean(view_count)),
median = round(median(view_count)))
df9<-maindata %>% group_by(danger) %>% summarise(mean = round(mean(view_count)),
median = round(median(view_count)))
df10<-maindata %>% group_by(animals) %>% summarise(mean = round(mean(view_count)),
median = round(median(view_count)))
df11<-maindata %>% group_by(use_sex) %>% summarise(mean = round(mean(view_count)),
median = round(median(view_count)))
df_1 <- merge(df7, df8,  by = "row.names", all = TRUE)
df_2 <- merge(df_1, df9,  by = "row.names", all = TRUE)
df_3 <- merge(df_2, df10,  by = "row.names", all = TRUE)
df_4 <- merge(df_3, df11,  by = "row.names", all = TRUE)
df_5 <- df_4[ -c(1:4) ]
df_5
```

### Final Comments





